"MetaboPi"

\section{Abstract}
Handling high-throughout metabolomics data demands high computing and storage resource.  

How to compute the data locally (without sending it to a high-performance server) with a budgeted device could be an interesting topic to explore. 
Because this would provide possibilities to protect privacies in home-appliance or fulfil the real-time analysis tasks in some extreme conditions (such as in polar region or some areas with poor Internet connectivity)


why do i do this? because in the future, metabolomics analysis could become smart-home appliance, such as smart toilet or smart mirror. 
people can get their metabolome examined daily in their home.
such a good vision raised several problems. data privacy problem and cost.
because metabolome is considered as personal privacy. therefore, leak these privacy could result in bad results. however, if computed locally, whether it's possible to control the cost.

In this study, we simulated a computing task. 


Not only limited to human metabolome for risk analysis. it could also be applied in the fridge for example, to detect microorganisms' characteristic metabolome.

in less developed countries, or in portable devices, transmitting the data could be very expensive (via satalliate for example, in polar areas), therefore, computing such a dataset whether it's possible. 

\section{Introduction}
\subsubsection{Potential Use environment}
\subsubsection{hello}

\section{Solution}

\section{Business Model}